---
title: "Alcohol vs Seat choice"
author: "Peter Dang"
date: "Spring 2025"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
 The median number of drinks in the back row is larger than the median of both the front and middle row, and we can see that by looking at the boxes, according to the boxplot shown.   
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

We can see that there are "bites" on the boxes that are on the boxplot above. These bites represent the standard deviation, which is the amount of deviations amongst the data. 

## Numerical Summarys 

## Inferential Tests

## Conclusions


