---
title: "Alcohol vs Seat choice"
author: "Peter Dang"
date: "Spring 2025"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
 The median number of drinks in the back row is larger than the median of both the front and middle row, and we can see that by looking at the boxes, according to the boxplot shown.   
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

We can see that there are "bites" on the boxes that are on the boxplot above. These bites represent the standard deviation, which is the amount of deviations amongst the data. 

## Numerical Summarys 
```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

According to the data above, we can see that the size of the box from the back goes from 0 to 12.5, the box from the front goes from 0 to 2, and the box from the middle goes from 0 to 4. 

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

## Conclusions
We reject the null hypothesis, because the number is very low, the data we have is 0.000116. 


```{r}
#we specify the margins starting at the bottom and proceeding clockwise - thus 8.7 is the left side margin to hold the names of the factors
par(mar = c(3, 8.7, 2, 2))
plot(TukeyHSD(model1),las=2)
```

According to the data above, we can see that 0 is in the confidence interval only between the front and the middle. Which means that the back is different than both of them. Therefore it shows that there is no statistical difference between the front and the middle. This is the case that both of them are the same and one of them is different from the others. 